Simulating spaces and stressors

### 2024-10-08 Analysis/01_Simulating_spaces_and_stressors.Rmd
Update 01_Simulating_spaces_and_stressors.Rmd

## First line
plot.text.box("A) Tree and trait\nsimulation:", cex = 2)
plot(simulated_data, main = "Tree and trait simulation\nunder a BM process (1D)", col = c("lightgrey", "blue"), ylab = "Trait 1")
plot(simulated_data, main = "Tree and trait simulation\nunder a BM process (2D)", col = c("lightgrey", "blue"), trait = c(1,2), xlab = "Trait 1", ylab = "Trait 2")

>>>>

## First line
plot.text.box("A) Tree and trait\nsimulation:", cex = 2)
plot(simulated_data, main = "Tree and trait simulation\nunder a BM process (1D)", col = c(tips = "blue", "nodes" = "lightgrey"), ylab = "Trait 1")
plot(simulated_data, main = "Tree and trait simulation\nunder a BM process (2D)", col = c("lightgrey", "blue"), trait = c(1,2), xlab = "Trait 1", ylab = "Trait 2")
